Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-28 ms.Rnw
minor edits

for (i in 1:3) {
  if (!dir.exists(paste0("model", i, '/', rl_dir))) {
    dir.create(paste0("model", i, '/', rl_dir), recursive = TRUE)
  }
}

@@

  # Global search, all parameters
  SEARCH1 <- list(
    NP = 1500, NMIF = 100, NREPS = 144, NREPS_EVAL = 36, NP_EVAL = 2000,
    RW_SD = rw.sd(
      betaB = 0.02,   # Unit Specific
      foi_add = 0.02, # Unit Specific
      mu_B = 0.02,
      thetaI = 0.02,
      XthetaA = 0.02,
      lambdaR = 0.02,
      r = 0.01,
      std_W = 0.02,
      epsilon = 0.02,
      k = 0.02,
      sigma = 0.02
    )
  )

  # Local search, all parameters
  SEARCH2 <- list(
    TOP_N = 12, NP = 2000, NMIF = 100, NREPS = 6, NREPS_EVAL = 36, NP_EVAL = 3000,
    RW_SD = rw.sd(
      betaB = 0.0075,   # Unit Specific
      foi_add = 0.0075, # Unit Specific
      mu_B = 0.0075,
      thetaI = 0.0075,
      XthetaA = 0.0075,
      lambdaR = 0.0075,
      r = 0.005,
      std_W = 0.0075,
      epsilon = 0.0075,
      k = 0.0075,
      sigma = 0.0075
    )
  )

  # Local search, unit specific parameters
  SEARCH3 <- list(
    TOP_N = 9, NP = 2000, NMIF = 100, NREPS = 8, NREPS_EVAL = 36, NP_EVAL = 4000,
    RW_SD = rw.sd(
      betaB = 0.005,
      foi_add = 0.005
    )
  )

>>>>

# run_level_* for model 2 is not needed.
for (i in c(1, 3)) {
  if (!dir.exists(paste0("model", i, '/', rl_dir))) {
    dir.create(paste0("model", i, '/', rl_dir), recursive = TRUE)
  }
}

if (!dir.exists('model2')) dir.create("model2/")

@@

  # Global search, all parameters

  SEARCH1 = list(
    NBPF = 100,
    NP = 1500,
    SPAT_REGRESSION = 0.5,
    NREPS = 144,
    NP_EVAL = 2000,
    NREPS_EVAL = 36
  )

  SEARCH2 = list(
    TOP_N = 12,
    NBPF = 100,
    NP = 2000,
    SPAT_REGRESSION = 0.5,
    NREPS = 6,
    NP_EVAL = 3000,
    NREPS_EVAL = 36
  )

  SEARCH3 = list(
    TOP_N = 9,
    NBPF = 100,
    NP = 2500,
    SPAT_REGRESSION = 0.5,
    NREPS = 8,
    NP_EVAL = 5000,
    NREPS_EVAL = 36
  )
